Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-20 cav2017/cav2017.tex
Sec 3.1

We consider physical models expressed as ordinary differential equations (ODEs) with full state information:  
%
\begin{align}
\label{eq:ode}
\dot{x}(t) = Ax(t)+ B u(t)\ \ :\ \ x \in \mathbb{R}^{n}, u \in \mathbb{R}^m, A \in \mathbb{R}^{n \times n}, B \in \mathbb{R}^{n \times m}
\end{align}
where $A$ and $B$ are matrices that fully specify the continuous plant.  
\todo{[specify initial conditions? specify input ranges already here? ]} 
Eq.~\eqref{eq:ode} is soundly discretised (as shown in the Appendix \todo{[there we can present directly the full LTI case with outputs]}) into
%
\begin{align}
\label{eq:plant}
x_{k+1} = A_d x_k+ B_d u_k. 
\end{align}
%

>>>>

We consider physical models expressed as ordinary differential equations (ODEs) with full state information:  
%
\begin{align}
\label{eq:ode}
\dot{x}(t) = Ax(t)+ B u(t)\ \ :\ \ x \in \mathbb{R}^{n}, u \in \mathbb{R}^m, A \in \mathbb{R}^{n \times n}, B \in \mathbb{R}^{n \times m}
\end{align}
where $A$ and $B$ are matrices that fully specify the continuous plant with the initial states $x(0)$. 
Eq.~\eqref{eq:ode} is soundly discretised (as shown in the Appendix) into
%
\begin{align}
\label{eq:plant}
x_{k+1} = A_d x_k+ B_d u_k 
y_{k} = C_d x_k+ D_d u_k,
\end{align}
with initial state $x_{0}=x(0)$.

%
